\chapter{\keyword{ADVENTURERS}}


\section{\keyword{ATTRIBUTES}}

Every \keyword{ADVENTURER} has \keyword{ATTRIBUTES}. The \keyword{ATTRIBUTES} determine the stats of the specific \keyword{ADVENTURER} and provide improvements and different capabilities when doing \keyword{MISSIONS}.

\subsection{\keyword{STRENGTH}}

\keyword{STRENGTH} represents the strength of an adventurer. This value will affect the success rate of all \keyword{MISSIONS} but has a greater affect on \keyword{BATTLE MISSIONS}, \keyword{RESCUE MISSIONS}, \keyword{ESCORT MISSIONS}, and \keyword{HUNTING MISSIONS}.

\subsection{\keyword{STAMINA}}

\keyword{STAMINA} represents the Stamina and Vitality of an adventurer. This value will affect the success rate of all \keyword{MISSIONS} but has a greater affect on longer \keyword{MISSIONS}, \keyword{EXPLORATION MISSIONS}, \keyword{MINING MISSIONS} and \keyword{SURVIVAL MISSIONS}.

\subsection{\keyword{AGILITY}}

\keyword{AGILITY} represents the Agility and Speed of an adventurer. This value will affect the success rate of all \keyword{MISSIONS} but has a greater affect on shorter \keyword{MISSIONS}, \keyword{DELIVERY MISSIONS}, \keyword{STEALTH MISSIONS}, and \keyword{SABOTAGE MISSIONS}.

\subsection{\keyword{INTELLIGENCE}}

\keyword{INTELLIGENCE} represents the Intelligence and Knowledge of an adventurer. This value will affect the success rate of all \keyword{MISSIONS} but has a greater affect on \keyword{TRACKING MISSIONS}, \keyword{RESEARCH MISSIONS}, \keyword{STRATEGIC MISSIONS}, and improves the chance of getting better rewards from any \keyword{MISSION}.

\subsection{\keyword{WISDOM}}

\keyword{WISDOM} represents the Wisdom and Intuition of an adventurer. This value will affect the success rate of all \keyword{MISSIONS} but has a greater affect on \keyword{DIPLOMATIC MISSIONS}, \keyword{SPIRITUAL MISSIONS}, \keyword{SUPPORT MISSIONS}, and improves the chance of getting more rewards for completing any \keyword{MISSION}.




\section{\keyword{EQUIPMENT}}

Each \keyword{ADVENTURER} has a set of \keyword{EQUIPMENT} which can improve the \keyword{ADVENTURER}'s stats or give them other abilities. These \keyword{EQUIPMENT} can help for better success of \keyword{MISSIONS} or for better rewards from \keyword{MISSIONS}.

\subsection{\keyword{WEAPON}}

A \keyword{WEAPON} is an item given to an \keyword{ADVENTURER}. The \keyword{WEAPON} can be one of many types and can provide different benefits depending on the type.

\begin{table}[h!]
\centering
\begin{tabular}{|l|l|p{10cm}|}
\hline
\textbf{\keyword{WEAPON} Type} & \textbf{Primary Attribute(s)} & \textbf{Effect} \\ \hline
\keyword{Sword} & \keyword{STRENGTH} &  \\ \hline
\keyword{Bow} & \keyword{AGILITY} &  \\ \hline
\keyword{Axe} & \keyword{STRENGTH} &  \\ \hline
\keyword{Pickaxe} & \keyword{STAMINA} &  \\ \hline
\keyword{Dagger} & \keyword{AGILITY} &  \\ \hline
\keyword{Staff} & \keyword{INTELLIGENCE} & \\ \hline
\keyword{Hammer} & \keyword{STAMINA} &  \\ \hline
\keyword{Warhammer} & \keyword{STRENGTH} &  \\ \hline
\keyword{Crossbow} & \keyword{AGILITY} &  \\ \hline
\keyword{Spear} & \keyword{STRENGTH} &  \\ \hline
\end{tabular}
\caption{Weapon Types and Their Benefits}
\end{table}


\subsection{\keyword{ARMOR}}

A \keyword{ARMOR} is an item given to an \keyword{ADVENTURER}. The \keyword{ARMOR} can be one of many types and can provide different benefits depending on the type. \keyword{ARMOR} can also be used to allow \keyword{MISSIONS} in certain \keyword{CLIMATES} to be completed.

\begin{table}[h!]
\centering
\begin{tabular}{|l|l|p{10cm}|}
\hline
\textbf{\keyword{ARMOR} Type} & \textbf{Effect} \\ \hline
\keyword{Plate Armor} & \\ \hline
\keyword{Leather Armor} & \\ \hline
\keyword{Chainmail} & Strength &  \\ \hline
\keyword{Cloak of Shadows} & \\ \hline
\keyword{Robes} &  \\ \hline
\keyword{Explorer's Gear} & \\ \hline
\keyword{Survivalist Armor} & \\ \hline
\keyword{Tunic} & \\ \hline
\keyword{Hunter's Garb} &  \\ \hline
\keyword{Wool Coat} &  \\ \hline
\end{tabular}
\caption{Armor Types and Their Benefits}
\end{table}

\subsection{\keyword{STEED}}


\begin{table}[h!]
\centering
\begin{tabular}{|l|l|p{10cm}|}
\hline
\textbf{\keyword{STEED} Type} & \textbf{Effect} \\ \hline
\keyword{Horse} & \\ \hline
\keyword{Donkey} & \\ \hline
\keyword{Sled Dogs} & \\ \hline
\end{tabular}
\caption{Armor Types and Their Benefits}
\end{table}

\subsection{\keyword{SPECIAL}}
