\chapter{\keyword{GARRISON}}

The \keyword{GARRISON} serves as the central hub where players manage their \keyword{ADVENTURERS} and \keyword{BUILDINGS}. It contains core facilities used to prepare \keyword{ADVENTURERS} for \keyword{MISSIONS}, produce necessary \keyword{RESOURCES}, and craft \keyword{ITEMS}. As the game progresses, players can construct additional \keyword{BUILDINGS} that offer various functions such as \keyword{CRAFTING}, resource generation, and adventurer training. Upgrading these \keyword{BUILDINGS} improves efficiency and unlocks new capabilities, contributing to the overall growth and success of the \keyword{ADVENTURERS} on their \keyword{MISSIONS}.

\section{Base/Starting \keyword{GARRISON}}

At the start of the game, the player begins with only a basic \keyword{MISSION HALL}, a basic \keyword{STOREHOUSE}, and one custom \keyword{ADVENTURER}. The basic \keyword{MISSION HALL} gives the player the ability to perform simple starting \keyword{MISSIONS}.

\section{\keyword{BUILDINGS}}

The primary units of the \keyword{GARRISON} are \keyword{BUILDINGS}. The players cna construct and upgrade \keyword{BUILDINGS} to unlock features and progress through the game. The \keyword{BUILDINGS} are all upgradeable by expending \keyword{RESOURCES} and doing so will improve the buildings functions and access new features. The \keyword{BUILDINGS} will also slowly evolve in design as they are upgraded.

\subsection{\keyword{MISSION HALL}}

The \keyword{MISSION HALL} is the main building of the \keyword{GARRISON}. The \keyword{MISSION HALL} allows the player to send their \keyword{ADVENTURERS} on various \keyword{MISSIONS} to collect \keyword{RESOURCES}. The player starts with this building and can upgrade it further using \keyword{RESOURCES} as they progress. 

\subsection{\keyword{LUMBER MILL}}

The \keyword{LUMBER MILL} is the first building the player will build as part of their \keyword{GARRISON}. The \keyword{LUMBER MILL} will be built during the tutorial stages of the game. This building is used to clear out the areas around the \keyword{GARRISON} to allow for expansion as well as a steady supply of \keyword{LUMBER} for the player. The players can hire more \keyword{LUMBERJACKS} from the \keyword{TAVERN} to work the \keyword{LUMBER MILL}.

\subsection{\keyword{STOREHOUSE}}

The \keyword{STOREHOUSE} is a simple building that provides storage for the players \keyword{RESOURCES}. This building can be upgraded continually to hold more items.

\subsection{\keyword{MINE}}

The \keyword{MINE} is a \keyword{BUILDING} which will allow the players to collect metals passively. The players can hire more \keyword{MINERS} from the \keyword{TAVERN} to work the \keyword{MINE}.

\subsection{\keyword{FARM}}

The \keyword{MINE} is a \keyword{BUILDING} which will allow the players to collect food passively. The players can hire more \keyword{FARMERS} from the \keyword{TAVERN} to work the \keyword{FARM}.

\subsection{\keyword{GARDEN}}

The \keyword{MINE} is a \keyword{BUILDING} which will allow the players to collect food and herbs passively. The players can hire more \keyword{GARDENERS} from the \keyword{TAVERN} to work the \keyword{GARDEN}.

\subsection{\keyword{ARCANE TOWER}}

The \keyword{ARCANE TOWER} provide a place for the \keyword{ADVENTURERS} to train the mind and spirit at. This allows an increase in \keyword{INTELLIGENCE} and \keyword{WISDOM} for the \keyword{ADVENTURERS}.

\subsection{\keyword{BLACKSMITH}}

The \keyword{BLACKSMITH} provides a plave for the player to forge \keyword{WEAPONS} for their \keyword{ADVENTURERS}. 

\subsection{\keyword{TRAINING GROUNDS}}

The \keyword{TRAINING GROUNDS} provide a place for the \keyword{ADVENTURERS} to train the body at. This allows an increase in \keyword{STRENGTH}, \keyword{STAMINA}, or \keyword{AGILITY} for the \keyword{ADVENTURERS}.

\subsection{\keyword{TAVERN}}

The \keyword{TAVERN} is a building which allows travelers to visit the players \keyword{GARRISON}. Some of these travelers include \keyword{LUMBERJACKS}, \keyword{MINERS}, \keyword{GARDENERS}, and \keyword{FARMERS} which can be hired by the player to work for them. The \keyword{TAVERN} will also have \keyword{ADVENTURERS} that visit which can be hired by the players.

\subsection{\keyword{TEMPLE}}

\subsection{\keyword{HUNTING LODGE}}

\subsection{\keyword{WORKSHOP}}

\subsection{\keyword{STABLES}}

\subsection{\keyword{DOCKS}}
